SNIK: Textbook Knowledge on Hospital Information Management as Linked Data

### 2020-08-21 paper.tex
Expand interlinking.
Improve and split details and statistics table.
Add performance statements to SNIK Graph.

%\usepackage{dcolumn}
%\usepackage{endnotes}
\usepackage{booktabs}
\usepackage{tabulary}
\usepackage{csquotes}
\usepackage{siunitx}
%\usepackage{graphicx}
\usepackage{todonotes}
%\usepackage{natbib} % does not seem to work with ios 1
\renewcommand{\citet}{\cite}% citet is not defined without natbib
\renewcommand{\citep}{\cite}% citep is not defined without natbib
\setlength{\marginparwidth}{2.1cm}% enough space for todonotes
\usepackage{listings}
\usepackage{aurl}
\daurl{bb}{http://www.snik.eu/ontology/bb/}
\daurl{meta}{http://www.snik.eu/ontology/meta/}
\lstset{language=SPARQL,breaklines=true}
\usepackage{cleveref}
\newcommand{\snikversion}{1.0}
\newcommand{\sniktriples}{\num{72046}}
\newcommand{\snikclasses}{\num{2655}}
\newcommand{\snikproperties}{\num{339}}
\newcommand{\sniklinks}{\num{581}}
%%%%%%%%%%% End of definitions

@@

\begin{table}
\caption{Statistics and Details}
\label{tab:namespaces}
\begin{tabulary}{\columnwidth}{lL}
\toprule
URL		&\url{http://www.snik.eu/ontology}\\
Version		&\snikversion{}\\
License		&CC BY-NC-SA 4.0\\
SPARQL Endpoint	&\url{http://www.snik.eu/sparql}\\
LOD Cloud	&\url{https://lod-cloud.net/dataset/snik}\\
Datahub		&\url{https://datahub.io/imise/snik/v/1}\\
Visualization	&\url{http://www.snik.eu/graph}\\
RDF Browser	&\url{http://www.snik.eu/ontology}\\
Download	&\url{https://github.com/IMISE/snik-ontology/releases/download/1.0.0/snik.zip}\\
\# Triples	&\sniktriples{}\\
\# Classes	&\snikclasses{}\\
\# Properties	&\snikproperties{}\\
\# Internal Links	&\num{360}\\
\# Links to HITO  	&\num{260}\\
\# Links to DBpedia 	&\sniklinks{}\\
%Subontologies	&\url{http://www.snik.eu/ontology/bb}\\
%		&\url{http://www.snik.eu/ontology/ciox,}\\
%		&\url{http://www.snik.eu/ontology/ob}\\
%		&\url{http://www.snik.eu/ontology/he}\\
%		&\url{http://www.snik.eu/ontology/it4it}\\
\bottomrule
\end{tabulary}%The source code for the services is available at \url{https://github.com/imise}
\end{table}

@@

\section{Lifecycle}\label{sec:application}

@@

\subsection{SNIK Graph}\label{sec:snik-graph}
\todo{reference franziskas poster in both figures}
\todo{get a higher quality version of overview graphic}
\todo{reference \citet{visualizationoflargeontologies}}

>>>>

%\usepackage{dcolumn}
%\usepackage{endnotes}
\usepackage{booktabs}
\usepackage{tabulary}
\usepackage{csquotes}
\usepackage{siunitx}
%\usepackage{graphicx}
\usepackage{todonotes}
%\usepackage{natbib} % does not seem to work with ios 1
\renewcommand{\citet}{\cite}% citet is not defined without natbib
\renewcommand{\citep}{\cite}% citep is not defined without natbib
\setlength{\marginparwidth}{2.1cm}% enough space for todonotes
\usepackage{listings}
\usepackage{aurl}
\daurl{bb}{http://www.snik.eu/ontology/bb/}
\daurl{meta}{http://www.snik.eu/ontology/meta/}
\lstset{language=SPARQL,breaklines=true}
\usepackage{cleveref}
\newcommand{\snikversion}{1.0}
\newcommand{\sniktriples}{72046}
\newcommand{\snikclasses}{2655}
\newcommand{\snikproperties}{339}
\newcommand{\sniklinks}{581}
%%%%%%%%%%% End of definitions

@@

\begin{table}
\caption{Access Options and Details}
\label{tab:access}
\begin{tabulary}{\columnwidth}{lL}
\toprule
URL		&\url{http://www.snik.eu/ontology}\\
Version		&\snikversion{}\\
License		&CC BY-NC-SA 4.0\\
SPARQL Endpoint	&\url{http://www.snik.eu/sparql}\\
LOD Cloud	&\url{https://lod-cloud.net/dataset/snik}\\
Datahub		&\url{https://datahub.io/imise/snik/v/1}\\
Visualization	&\url{http://www.snik.eu/graph}\\
RDF Browser	&\url{http://www.snik.eu/ontology}\\
Download	&\url{https://github.com/IMISE/snik-ontology/releases/download/1.0.0/snik.zip}\\
\bottomrule
\end{tabulary}%The source code for the services is available at \url{https://github.com/imise}
\end{table}

\begin{table}
\caption{Statistics}
\label{tab:statistics}
\begin{tabulary}{\columnwidth}{lS}
\toprule
Nr. of Triples			&\sniktriples{}\\
Nr. of Classes			&\snikclasses{}\\
Nr. of Properties		&\snikproperties{}\\
Nr. of Internal Links		&360\\
Nr. of Links to HITO  		&260\\
Nr. of Links to DBpedia 	&\sniklinks{}\\
%Subontologies	&\url{http://www.snik.eu/ontology/bb}\\
%		&\url{http://www.snik.eu/ontology/ciox,}\\
%		&\url{http://www.snik.eu/ontology/ob}\\
%		&\url{http://www.snik.eu/ontology/he}\\
%		&\url{http://www.snik.eu/ontology/it4it}\\
\bottomrule
\end{tabulary}%The source code for the services is available at \url{https://github.com/imise}
\end{table}

@@

\section{Data Transformation Process}
\subsection{Interlinking}
%As shown in \cref{...}, we aligned our dataset to several others:
We manually aligned our dataset to HITO, the Health IT Ontology~\citep{hito}
We automatically aligned our dataset to:
- DBpedia~\citep{dbpedia}, as  
- 
\section{Lifecycle}\label{sec:application}

@@

\subsection{SNIK Graph}\label{sec:snik-graph}
\paragraperformance
due to the limitations of JavaScript (e.g. single threaded), which are hard to work around, which leads to performance problems with the library Cytoscape.js which is the base of the graph visualization, on very large ontologies / graphs.
right now we have 2641 nodes and 4904 edges and the performance is ok in Chrome but not amazing.
with 10000 nodes it would probably be too slow on most machines.

\todo{reference franziskas poster in both figures}
\todo{get a higher quality version of overview graphic}
\todo{reference \citet{visualizationoflargeontologies}}
